### 2018-04-26 papers/synth/encoding.tex
encoding formula fix

%
%
\begin{enumerate}[label=\Alph*]
\item  Add new edges to the given VTS to achieve graph stability, fusion and k connected. 
\item  Modify the flow of molecules on the nodes and on the edges.
  \begin{enumerate}
  	\item use available set of molecules.
    \item allow new molecule type to be added.     
  \end{enumerate}        
\item Learning meaningful activity functions from a given language of
  propositional formulas
  \begin{enumerate}
    \item kcnf: low depth circuit.
    \item Boolean gates: And, Or.
    \item Boolean gates with linear combination.  
    \end{enumerate}        
  % - Function dependence with var occurring once.
\item  VTS repair. [Allow both delete and add to the system]
\end{enumerate}

@@

The basicvtsconstraints and vtsactivityconstraint are same as the
previous sections, describing stability of the graph and fusion of the
edge into the node and the molecular activity describing the active
state of a molecule. The givenvtsinformation is encoded using a front
end input language. The user provides the information of the VTS with
a partial information using this front end. Our tool then converts
these inputs into the constraints over the given VTS.

We encode the restriction\_on\_modification by putting the constraints on the unassigned edges and edge labels. The constraint of allowing only certain number of addition to the given VTS is encoded as at\_most\_k() function over the unassigned edges and label.

\begin{align}
    constraint on edge = atmost\_k\_allowed ( unassigned edges in VTS )    
    constraints of the molecular activity on the edge = at\_most\_k ( unassigned activity labels in VTS edges )
    constraints of the molecule presence on the edge = at\_most\_k ( unassigned molecule labels in VTS edges )\label{eq:addedge2}
\end{align}

@@

\begin{align}
 \exists e_{ijq} ( connectivity\_constraint && self\_edge\_restriction && \ref{eq:addedge1} )    
  \tag{E1}\label{eq:addedge2}
\end{align}

The connectivity\_constraint \&\& self\_edge\_restriction are same as the previous sections, describing the graph to be a k but not k+1 connected and self edges are not allowed in the VTS. addedge1 is the constraint of \ref{eq:addedge1}.

@@

    auto addConstraints = edgeC \&\& edgeActivityC \&\& edgePresenceC  \&\& fixVar0;

    auto qvtsCons = exists( setN, 
                    exists( setActiveN, 
                    exists( setPresenceE,  
                    exists( setActiveE, 
                    exists( setPairingM, 
                    exists( setReach, 
                            vtsCons \&\& vtsActivity \&\& inputCons \&\& addConstraints ))))));

>>>>

%
%
\begin{enumerate}[label=\Alph*]
\item  Add new edges to the given VTS to achieve k-connectivity, graph stability and fusion. 
\item  Modify the flow of molecules on the nodes and on the edges.
  \begin{enumerate}
  	\item use available set of molecules.
    \item allow new molecule type to be added.     
  \end{enumerate}        
\item Learning meaningful activity functions from a given language of
  propositional formulas
  \begin{enumerate}
    \item kcnf: low depth circuit.
    \item Boolean gates: And, Or.
    \item Boolean gates with linear combination.  
    \end{enumerate}        
  % - Function dependence with var occurring once.
\item  VTS repair. Allow both delete and add to the system.
\end{enumerate}

@@

%The basicvtsconstraints and vtsactivityconstraint are same as the
The \texttt{Consistancy} describing stability of the graph and fusion of the
edge into the node and the molecular activity describing the active
state of a molecule. The \texttt{GivenCons} is encoded using a front
end input language. The user provides the information of the VTS with
a partial information using this front end. Our tool then converts
these inputs into the constraints over the given VTS.

We encode the \texttt{ModifyCons} by putting the constraints on the unassigned edges and edge labels. The constraint of allowing only certain number of addition to the given VTS is encoded as \texttt{AtMostK} function over the unassigned edges and label.

%\[Unassigned Edges\]}
%\[Unassigned Activity Labels\]} 
%\[Unassigned Molecule Labels\]
\begin{align}
   \texttt{EdgeConstraint} = \texttt{AtMostk} \, [ \texttt{unassigned\_edges} ]  
   \tag{E2}\label{eq:addedge2}
\end{align}
\begin{align}
   \texttt{EdgeActivity} = \texttt{AtMostK} \, [ \texttt{activity\_labels} ]
   \tag{E3}\label{eq:addedge3}
\end{align}

\begin{align}
   \texttt{EdgePresence} = \texttt{AtMostK} \, [ \texttt{unassigned\_molecule\_labels} ]  
   \tag{E4}\label{eq:addedge4}
\end{align}

@@

\begin{align}
  \exists i, j, q \,
  ( \texttt{KConnectivity}  \land \texttt{NoSelfEdge} \land \ref{eq:addedge1} )    
  \tag{E5}\label{eq:addedge5}
\end{align}

The \texttt{KConnectivity} and \texttt{NoSelfEdge} are same as the previous section, describing the graph to be a k but not k+1 connected and self edges are not allowed in the VTS. addedge1 is the constraint of \ref{eq:addedge1}.

@@

 %   auto addConstraints = edgeC \&\& edgeActivityC \&\& edgePresenceC  \&\& fixVar0;

% %   auto qvtsCons = exists( setN, 
%                    exists( setActiveN, 
%                    exists( setPresenceE,  
%                    exists( setActiveE, 
%                    exists( setPairingM, 
%                    exists( setReach, 
%                            vtsCons \&\& vtsActivity \&\& inputCons \&\& addConstraints ))))));
